Human Factors Influencing Visual Statistical Inference

### 2013-06-13 sociology_paper.tex
demographic model result added

>>>>

\begin{table}[htbp]
\centering
\caption{Parameter estimates of Model \eqref{eqn:model_demo} fitted for avarage log time taken and probability of correct lineup evaluation.}
\scalebox{0.9}{
\begin{tabular}{rrrrrrrrrrr}
  \hline
& \multicolumn{4}{c} {Log(Time)} & &\multicolumn{4}{c} {Proportion correct} \\

\cline{2-5} \cline{7-10} 
 Effect& Est & SE & Zval & $p$-value && Est & SE & Zval & $p$-value  \\ 
  \hline
Fixed &  &  &  & && &  &  \\ 
$\mu$ & 3.465 & 0.014 & 241.52 & $<$0.001 &   & -0.834 & 0.073 & -11.43 & $<$0.001 \\ 
\multicolumn{2}{l}{Age}   &  &  &  &  & & && \\   
  26-30 & 0.058 & 0.013 & 4.50 & $<$0.001 &   & 0.062 & 0.049 & 1.27 & 0.209 \\ 
  31-35 & 0.068 & 0.014 & 4.72 & $<$0.001 &   & 0.115 & 0.055 & 2.08 & 0.038 \\ 
  36-40 & 0.231 & 0.016 & 14.05 & $<$0.001 &   & 0.310 & 0.063 & 4.93 & $<$0.001 \\ 
  41-45 & 0.176 & 0.021 & 8.56 & $<$0.001 &   & 0.158 & 0.081 & 1.96 & 0.050 \\ 
  46-50 & 0.272 & 0.024 & 11.29 & $<$0.001 &   & 0.141 & 0.096 & 1.47 & 0.143 \\ 
  above 50 & 0.352 & 0.018 & 19.19 & $<$0.001 &   & 0.147 & 0.071 & 2.06 & 0.039 \\ 
\multicolumn{2}{l}{Country}   &  &  &  &  & & && \\   
  Rest world & -0.086 & 0.016 & -5.52 & $<$0.001 &   & 0.267 & 0.060 & 4.49 & $<$0.001 \\ 
  USA & -0.230 & 0.012 & -19.39 & $<$0.001 &   & 0.186 & 0.046 & 4.05 & $<$0.001 \\ 
\multicolumn{2}{l}{Education}   &  &  &  &  & & && \\       
  UG course & 0.042 & 0.013 & 3.25 & 0.0011 &   & -0.083 & 0.050 & -1.65 & 0.098 \\ 
  UG degree & -0.037 & 0.012 & -3.21 & 0.0013 &   & -0.044 & 0.045 & -0.97 & 0.330 \\ 
  Gr. course & 0.117 & 0.013 & 9.12 & $<$0.001 &   & 0.070 & 0.050 & 1.42 & 0.157 \\ 
  Gr. degree & 0.046 & 0.011 & 4.12 & $<$0.001 &   & 0.182 & 0.043 & 4.22 & $<$0.001 \\ 
\multicolumn{2}{l}{Gender}   &  &  &  &  & & && \\     
  Male & 0.078 & 0.009 & 8.26 & $<$0.001 &   & 0.055 & 0.036 & 1.50 & 0.133 \\ 
\multicolumn{2}{l}{Random}   &  &  &  &  & & && \\ 
  Lineup & 0.082 & 0.287 &  &  &   & 5.259 & 2.293 &  &  \\ 
  Error & 0.479 & 0.692 &  &  & & && &\\ 
   \hline
\end{tabular}
}
\label{tbl:model_result_demographics}
\end{table}

%\begin{table}[ht]
%\centering
%\begin{tabular}{rrrlllrrll}
%  \hline
% & Est & SE & Zval & pvalue & g1 & Est & SE & Zval & pvalue \\ 
%  \hline
%(Intercept) & 3.465 & 0.014 & 241.52 & $<$0.001 &   & -0.834 & 0.073 & -11.43 & $<$0.001 \\ 
%  age_level26-30 & 0.058 & 0.013 & 4.5 & $<$0.001 &   & 0.062 & 0.049 & 1.27 & 0.2058 \\ 
%  age_level31-35 & 0.068 & 0.014 & 4.72 & $<$0.001 &   & 0.115 & 0.055 & 2.08 & 0.0375 \\ 
%  age_level36-40 & 0.231 & 0.016 & 14.05 & $<$0.001 &   & 0.310 & 0.063 & 4.93 & $<$0.001 \\ 
%  age_level41-45 & 0.176 & 0.021 & 8.56 & $<$0.001 &   & 0.158 & 0.081 & 1.96 & 0.0501 \\ 
%  age_level46-50 & 0.272 & 0.024 & 11.29 & $<$0.001 &   & 0.141 & 0.096 & 1.47 & 0.1425 \\ 
%  age_levelabove 50 & 0.352 & 0.018 & 19.19 & $<$0.001 &   & 0.147 & 0.071 & 2.06 & 0.0394 \\ 
%  countryRest of the world & -0.086 & 0.016 & -5.52 & $<$0.001 &   & 0.267 & 0.060 & 4.49 & $<$0.001 \\ 
%  countryUnited States & -0.230 & 0.012 & -19.39 & $<$0.001 &   & 0.186 & 0.046 & 4.05 & 1e-04 \\ 
%  degree.L & 0.042 & 0.013 & 3.25 & 0.0011 &   & -0.083 & 0.050 & -1.65 & 0.098 \\ 
%  degree.Q & -0.037 & 0.012 & -3.21 & 0.0013 &   & -0.044 & 0.045 & -0.97 & 0.3306 \\ 
%  degree.C & 0.117 & 0.013 & 9.12 & $<$0.001 &   & 0.070 & 0.050 & 1.42 & 0.1566 \\ 
%  degree^4 & 0.046 & 0.011 & 4.12 & $<$0.001 &   & 0.182 & 0.043 & 4.22 & $<$0.001 \\ 
%  gender_levelMale & 0.078 & 0.009 & 8.26 & $<$0.001 &   & 0.055 & 0.036 & 1.5 & 0.1329 \\ 
%  pic_name (Intercept) & 0.082 & 0.287 &  &  &   & 5.259 & 2.293 &  &  \\ 
%   \hline
%\end{tabular}
%\end{table}
